---
title: "Starbucks tidytuesday"
author: "Hui Yi Xuan"
date: "2023-01-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This is the Official Starbucks Nutritional dataset from the pdf Starbucks Coffee 
Company Beverage Nutrition Information. 


## Plot 1 

The insight we obtained from this graph is that the amount of caffeine is associated 
to calories content in Starbucks drinks. There is a greater likelihood that if a 
cup of coffee has more calories, the amount of caffeine (mg) is lesser too. 

The target audience are technical audience who might be interested in the trends
of the drinks Starbucks offers. 

geom_point is chosen to represent the many points so that it is easier for 
observations of the widespread amount of drinks. 
geom_smooth is chosen to map out the correlation more clearly for the viewer. 

A different shade of red is chosen to represent the varying amount of caffeine
for the drinks so that it will be easier to observe, would be helpful especially
since Starbucks is well-known for its coffee, hence it is assumed that most of 
their consumers will go for the drinks with higher caffeine. 



```{r}

library(tidyverse)
library(ggplot2)


tuesdata <- tidytuesdayR::tt_load('2021-12-21')
tuesdata <- tidytuesdayR::tt_load(2021, week = 52)

starbucks <- tuesdata$starbucks


starbucks <- starbucks %>%
  group_by(product_name) %>%
  mutate(max_serv_size = max(serv_size_m_l), max_cal = max(calories)) 

sbuck <- starbucks %>%
  filter(serv_size_m_l == max_serv_size & calories == max_cal) %>%
  group_by(product_name) %>%
  slice(1) %>%
  filter(size != "1 scoop")

ggplot(sbuck, aes(x=caffeine_mg, y=max_cal))+
  geom_point(aes(color = max_cal), position = "jitter") + 
  scale_color_gradient(low="pink", high = "red") +
  labs(x= "Calories", y= "Caffeine(mg)", title= "Caffeine vs Calories content in Starbucks Drinks") +
  geom_smooth(method=lm) +
  theme_light()
 
  
```

## Plot 2 
The insight we obtained from this graph is that the more sugar added to each drink, 
the amount of calories is higher too. 

The target audience are layman audience who might be interested to check the content
of their drinks before deciding which product to purchase from starbucks.  This is 
especially so for health consicious drinkers. 

While the graphs might be too small as there are many drinks, I chose to compromise
that and illustrate all drinks because it would be helpful if all drinks are 
featured especially since our target audience are consumers who are deciding 
which drink to buy, or who would like to check out and compare the few of their
favourite drinks. 

```{r }
starbucks %>% 
  mutate(
    product_name = factor(product_name),
    product_name = fct_reorder(product_name, calories)
  ) %>% 
  filter(calories > 200)  %>% 
  ggplot(aes(x = sugar_g, y = calories, color = product_name)) +
  geom_point(size = 1, shape = 5) +
  facet_wrap(~product_name, labeller = label_wrap_gen(15)) +
  theme_void(base_size = 4) +
  theme(
    text = element_text(color = "black", size = 5),
    axis.title.y = element_text(angle = 90),
    axis.title.x = element_text(size = 5),
    axis.text.y = element_text(size = 5),
    legend.position = "none",
    panel.spacing = unit(3, "lines"),
    plot.margin = margin(10, 10, 10, 10),
    plot.caption = element_text(hjust = 0)
  ) +
  labs(title = "Calories vs Sugar added", y = "Calories (kcal)", x = "Sugar (g)")

```